Comparison of delivering limited fault tolerance via publish-subscribe messaging and message queuing in asynchronous distributed systems

### 2018-11-10 latex/article.tex
table update

\subsubsection{Feature table}
\begin{table}[h]
\begin{tabular}{@{}lll@{}}
\toprule
Feature                                                                                                  & Publish-subscribe     & Message queue         \\ \midrule
Recovery from service failure                                                                            & \multicolumn{1}{c}{•} & \multicolumn{1}{c}{•} \\ \midrule
\begin{tabular}[c]{@{}l@{}}Adding subscribers without\\ modifications to rest of the system\end{tabular} & \multicolumn{1}{c}{•} &                       \\ \midrule
\begin{tabular}[c]{@{}l@{}}Allow subscribers to\\ control inbound message flow\end{tabular}              &                       & \multicolumn{1}{c}{•} \\ \midrule
\begin{tabular}[c]{@{}l@{}}Allow event system to\\ control outgoing message flow\end{tabular}            & \multicolumn{1}{c}{•} &                       \\ \midrule
\begin{tabular}[c]{@{}l@{}}Store identical messages\\ only once\end{tabular}                             & \multicolumn{1}{c}{•} &                       \\ \midrule
\begin{tabular}[c]{@{}l@{}}Secure communication\\ between publisher and subscriber\end{tabular}          &                       & \multicolumn{1}{c}{•} \\ \midrule
Non-exposed subscribers                                                                                  &                       & \multicolumn{1}{c}{•} \\ \bottomrule
\end{tabular}
\end{table}

\subsection{Second perspective: performance comparison}
In building an advertisement network that delivers content to over a billion devices, performance has been identified as a critical part of the system. Closely tied to general performance are lower latencies that have been observed to increase profits and advance customer satisfaction SOME REFS YO. Therefor having insight into performance differences is essential knowledge when business decisions are being made regarding the choice of an even system.
The following subsections will present concrete benchmarks and give a brief analysis on each one to better explain the differences.

>>>>

\subsubsection{Feature table}
\begin{table}[h]
\begin{tabular}{@{}lll@{}}
\toprule
Feature                                                                                                  & Publish-subscribe     & Message queue         \\ \midrule
Recovery from service failure                                                                            & \multicolumn{1}{c}{\textbullet} & \multicolumn{1}{c}{\textbullet} \\ \midrule
\begin{tabular}[c]{@{}l@{}}Adding subscribers without\\ modifications to rest of the system\end{tabular} & \multicolumn{1}{c}{\textbullet} &                       \\ \midrule
\begin{tabular}[c]{@{}l@{}}Allow subscribers to\\ control inbound message flow\end{tabular}              &                       & \multicolumn{1}{c}{\textbullet} \\ \midrule
\begin{tabular}[c]{@{}l@{}}Allow event system to\\ control outgoing message flow\end{tabular}            & \multicolumn{1}{c}{\textbullet} &                       \\ \midrule
\begin{tabular}[c]{@{}l@{}}Store identical messages\\ only once\end{tabular}                             & \multicolumn{1}{c}{\textbullet} &                       \\ \midrule
\begin{tabular}[c]{@{}l@{}}Secure communication\\ between publisher and subscriber\end{tabular}          &                       & \multicolumn{1}{c}{\textbullet} \\ \midrule
Non-exposed subscribers                                                                                  &                       & \multicolumn{1}{c}{\textbullet} \\ \bottomrule
\end{tabular}
\end{table}

\subsection{Second perspective: performance comparison}
In building an advertisement network that delivers content to over a billion devices, performance has been identified as a critical part of the system. Closely tied to general performance are lower latencies that have been observed to increase profits and advance customer satisfaction SOME REFS YO. Therefor having insight into performance differences is essential knowledge when business decisions are being made regarding the choice of an even system.
The following subsections will present concrete benchmarks and give a brief analysis on each one to better explain the differences.
\\
